Analysis-ready VCF at Biobank scale using Zarr

### 2025-03-05 paper.tex

The VCF Zarr specification is available on GitHub at
\url{https://github.com/sgkit-dev/vcf-zarr-spec/}.
The SAIGE prototype is available at \url{https://github.com/Will-Tyler/SAIGE}
and all other code for running benchmarks, analyses and creating
plots in this article is available at
\url{https://github.com/sgkit-dev/vcf-zarr-publication}.
Vcf2zarr is freely available under the terms of the Apache 2.0
license as part of the \texttt{bio2zarr}
suite (\url{https://github.com/sgkit-dev/bio2zarr/})
and can be installed from the Python Package Index
(\url{https://pypi.org/project/bio2zarr/}).
Vcztools (\url{https://github.com/sgkit-dev/vcztools/})
is freely available under the terms of the Apache 2.0
license and can be installed from the Python Package Index
(\url{https://pypi.org/project/vcztools/}).

>>>>

The VCF Zarr specification is available on GitHub at
\url{https://github.com/sgkit-dev/vcf-zarr-spec/}.
The SAIGE prototype is available at \url{https://github.com/Will-Tyler/SAIGE}
and all other code for running benchmarks, analyses and creating
plots in this article is available at
\url{https://github.com/sgkit-dev/vcf-zarr-publication}.
Vcf2zarr is freely available under the terms of the Apache 2.0
license as part of the \texttt{bio2zarr}
suite (\url{https://github.com/sgkit-dev/bio2zarr/}; 
biotoolsID=bio2zarr; RRID=SCR\_026481)
and can be installed from the Python Package Index
(\url{https://pypi.org/project/bio2zarr/}).
Vcztools (\url{https://github.com/sgkit-dev/vcztools/};
biotoolsID=vcztools; RRID=SCR\_026482)
is freely available under the terms of the Apache 2.0
license and can be installed from the Python Package Index
(\url{https://pypi.org/project/vcztools/}).
